\texttt{\Large{pyannote.metrics}}: a toolkit for reproducible evaluation,\\ diagnostic, and error analysis of speaker diarization systems

### 2017-03-17 paper.tex
fix: remove equation number

\begin{equation}
  \text{detection error rate} = \frac{\text{false alarm} + \text{missed detection}}{\text{total}}
\end{equation}
where $\text{false alarm}$ is the duration of non-speech incorrectly classified as speech, $\text{missed detection}$ is the duration of
speech incorrectly classified as non-speech, and $\text{total}$ is the total duration of speech in the reference.
Note that these metrics do not take overlapping speech into account.
In other words, overlapping speech regions are counted only once.

>>>>

\begin{equation*}
  \text{detection error rate} = \frac{\text{false alarm} + \text{missed detection}}{\text{total}}
\end{equation*}
where $\text{false alarm}$ is the duration of non-speech incorrectly classified as speech, $\text{missed detection}$ is the duration of
speech incorrectly classified as non-speech, and $\text{total}$ is the total duration of speech in the reference.
Note that these metrics do not take overlapping speech into account.
In other words, overlapping speech regions are counted only once.
